---
title: "p8105_hw6_wx2233"
author: "Weijia Xiong"
date: "11/15/2019"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom", text = element_text(size = 15), axis.title.x = element_text(size = 15)))

set.seed(1)
```



## Problem 1

### Load and clean the data
```{r}
birthweight = 
  read.csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  mutate(
    babysex = recode(babysex,"1" = "male",  "2" = "female") %>% 
      as.factor(),
    frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other","9" = "Unknown") %>% 
      as.factor(),
    malform = recode(malform, "0" = "absent", "1" = "present") %>% 
      as.factor(),
    mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other") %>% 
      as.factor()
  )
    
```



### Propose a regression model

Initial model: 
```{r}
fit1  = lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + menarche + momage + mheight + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = birthweight)
summary(fit1)
```
First I built a model using lots of factors, then I remove some inappropriate factors(collinearity or not significant) and add interactions to rebuild the model.

Rebuilt the model:
```{r}
fit2  = lm(bwt ~ babysex * bhead * blength + delwt + gaweeks + ppbmi + smoken, data = birthweight)
summary(fit2)
fit2 %>% 
  broom::tidy() %>% 
  knitr::kable()
```

### Plot of residuals against fitted values
```{r}
birthweight %>% 
  add_residuals(fit2) %>% 
  add_predictions(fit2) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  labs(
    x = "Fitted Values",
    y = "Residuals",
    title = "Residuals against Fitted Values"
  ) +
  geom_line( y = 0, color = "red")

```
The Residuals bounce around 0. But the variances of residuals are not constant.


### Compare your model to two others:


```{r}
fit3  = lm(bwt ~ blength + gaweeks, data = birthweight)
summary(fit3)
fit3 %>% 
  broom::tidy() %>% 
  knitr::kable()
```

```{r}
fit4  = lm(bwt ~ babysex * bhead * blength, data = birthweight)
summary(fit4)
fit4 %>% 
  broom::tidy() %>% 
  knitr::kable()
```

### Cross - Validation
```{r}
cv_df =
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(my_mod = map(train, ~fit2),
         main_mod = map(train, ~fit3),
         interaction_mod = map(train, ~fit4)) %>% 
  mutate(rmse_my = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
         rmse_main    = map2_dbl(main_mod, test, ~rmse(model = .x, data = .y)),
         rmse_interaction = map2_dbl(interaction_mod, test, ~rmse(model = .x, data = .y))
         )

cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin(aes(fill = model), alpha = .4)
  
```

From the plot we could see that the rmse of main model is the highest. And my model's rmse is lowest. It might indicates that my model fits better.


## Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```



### Bootstrap
```{r}
estimate_fun = function(mod){
  mod_results =
    mod %>% 
    broom::tidy()
  tibble(
    r_squared = pull(mod %>% broom::glance(),adj.r.squared),
    log_result = log(pull(mod_results,estimate)[1] * pull(mod_results,estimate)[2]),
  )
}

weather_results = 
 weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, estimate_fun)) %>% 
  unnest(results)

weather_results %>% 
  head(5)
```

### Distribution of two estimate quantities
```{r}
mean_and_sd = function(x) {
  estimate_mean = mean(x)
  estimate_sd = sd(x)
  tibble(
    estimate_mean,
    estimate_sd
  )
}

estimate_results = 
weather_results %>% 
  select(-strap,-.id,-models) %>% 
  map(~mean_and_sd(.)) %>% bind_rows() %>% 
  mutate(
    quantity = c("r_squared","logbeta01")
  ) %>% 
  select(quantity,everything())

estimate_results %>% 
  knitr::kable(digits = 4)
```

The mean of r square is `r round(pull(estimate_results,estimate_mean)[1],4)`, the sd of r square is `r round(pull(estimate_results,estimate_sd)[1],4)`, which shows that the r square is high, the model is explainable.

The mean of log(beta0beta1) is `r round(pull(estimate_results,estimate_mean)[2],4)`, the sd of log(beta0beta1) is `r round(pull(estimate_results,estimate_sd)[2],4)`.

The r_squared is a little left skewed(almost normal).
```{r}
weather_results %>% 
  ggplot(aes(x = r_squared, y = ..density..)) +
  geom_histogram(binwidth = 0.001, position = "dodge",fill = "#FF9999") +
  geom_density(alpha = .4, adjust = .5, color = "#FF9999",fill = "#FF9999")
```

The log(beta0beta1)  is almost normal distributed.

```{r}

weather_results %>% 
  ggplot(aes(x = log_result, y = ..density..)) +
  geom_histogram(binwidth = 0.002, position = "dodge",fill = "#99CCFF") +
  geom_density(alpha = .4, adjust = .5, color = "#99CCFF",fill = "#99CCFF") +
  labs(
    x = "log(beta0*beta1)"
  )
```

calculate a 95% confidence interval:

```{r}
CI_result = 
  tibble(
    Conf_int = c("lwr","upr"),
    CI_R_2 = quantile(pull(weather_results,r_squared), probs = c(0.025, 0.975),na.rm = TRUE),
    CI_logbeta01 =  quantile(pull(weather_results,log_result), probs = c(0.025, 0.975), na.rm = TRUE)
  )
  
CI_result %>% 
   knitr::kable(digits = 3)
```





