---
title: "p8105_hw6_wx2233"
author: "Weijia Xiong"
date: "11/15/2019"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom", text = element_text(size = 15), axis.title.x = element_text(size = 15)))

set.seed(1)
```



## Problem 1

### Load and clean the data
```{r}
birthweight = 
  read.csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  mutate(
    babysex = recode(babysex,"1" = "male",  "2" = "female") %>% 
      as.factor(),
    frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other","9" = "Unknown") %>% 
      as.factor(),
    malform = recode(malform, "0" = "absent", "1" = "present") %>% 
      as.factor(),
    mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other") %>% 
      as.factor()
  )
    
```



### Propose a regression model

Initial model: 
```{r}
fit1  = lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + menarche + momage + mheight + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = birthweight)
summary(fit1)
```
First I built a model using lots of factors, then I remove some inappropriate factors(collinearity or not significant) and add interactions to rebuild the model.

Rebuilt the model:
```{r}
fit2  = lm(bwt ~ babysex * bhead * blength + delwt + gaweeks + ppbmi + smoken, data = birthweight)
summary(fit2)
fit2 %>% 
  broom::tidy() %>% 
  knitr::kable()
```

### Plot of residuals against fitted values
```{r}
birthweight %>% 
  add_residuals(fit2) %>% 
  add_predictions(fit2) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  labs(
    x = "Fitted Values",
    y = "Residuals",
    title = "Residuals against Fitted Values"
  ) +
  geom_line( y = 0, color = "red")

```



### Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)

```{r}
fit3  = lm(bwt ~ blength + gaweeks, data = birthweight)
summary(fit3)
fit3 %>% 
  broom::tidy()
```


One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
fit4  = lm(bwt ~ babysex * bhead * blength, data = birthweight)
summary(fit4)
fit4 %>% 
  broom::tidy()
```

### Cross - Validation
```{r}
cv_df =
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(my_mod = map(train, ~fit2),
         main_mod = map(train, ~fit3),
         interaction_mod = map(train, ~fit4)) %>% 
  mutate(rmse_my = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
         rmse_main    = map2_dbl(main_mod, test, ~rmse(model = .x, data = .y)),
         rmse_interaction = map2_dbl(interaction_mod, test, ~rmse(model = .x, data = .y))
         )

cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
  
```


From the plot we could see that the rmse of main model is the highest. And my model's rmse is lowest. It might indicates that my model fits better.




## Problem 2
```{r}

```

